Motor Learning Without Moving: Proprioceptive and Predictive Hand Localization After Passive Visuoproprioceptive Discrepancy Training

### 2018-12-05 paper/paper.Rmd
removed dollars
changed ethics for plos

Twenty-five right-handed participants were recruited for this study. One participant was excluded for not following task instructions, and three were excluded for low performance on a task that ensures attention during the passive training. All analyses presented here pertain to the remaining twenty-one participants (13 females and 8 males, mean age: 20.1 +/- 2.3 years), but the data of the three low-performing participants is included in the online \href{https://osf.io/zfdth}{dataset} @Mostafa2017. All had normal or corrected-to-normal vision, and provided prior, written informed consent in accordance with the ethical guidelines set by the York Human subjects Review Subcommittee and received credit toward an undergraduate psychology course. Participants were screened verbally, and all reported being right handed and not having any history of visual, neurological, and/or motor dysfunction.

@@

$

@@

\begin{tablenotes}
\item 
\end{tablenotes}
\end{threeparttable}
\end{table}
$

>>>>

Twenty-five right-handed participants were recruited for the passive learning task in this study. One participant was excluded for not following task instructions, and three were excluded for low performance on a task that ensures attention during the passive training. All analyses presented here pertain to the remaining twenty-one participants (13 females and 8 males, mean age: 20.1 +/- 2.3 years), but the data of the three low-performing participants is included in the online \href{https://osf.io/zfdth}{dataset} @Mostafa2017. Participants provided prior, written informed consent in accordance with the ethical guidelines set by the York Human subjects Review Subcommittee (#2014-240). All had normal or corrected-to-normal vision, and received credit toward an undergraduate psychology course. Participants were screened verbally, and all reported being right handed and not having any history of visual, neurological, and/or motor dysfunction.  Published data from 21 further participants is used for comparison @Hart2016.

@@

@@

\begin{tablenotes}
\item 
\end{tablenotes}
\end{threeparttable}
\end{table}
